---
output: github_document
---

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/moodymudskipper/flow.svg?branch=master)](https://travis-ci.org/moodymudskipper/flow)
[![Codecov test coverage](https://codecov.io/gh/moodymudskipper/flow/branch/master/graph/badge.svg)](https://codecov.io/gh/moodymudskipper/flow?branch=master)
<!-- badges: end -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# flow

Visualize as flow diagrams the logic of functions, expressions or scripts and ease debugging.

* Call `flow_view()` on a function, a quoted expression, or the path of an R script
to visualize it.

* Call `flow_run()` on a call to a function to visualize which logical path in the
code was taken. Set `browse = TRUE` to debug your function block by block 
(similar to `base::browser()`) as the diagram updates.

* Export to *html*, *png*, *jpeg*, or *pdf*.

* Use the Rstudio addins to run `flow_view()` or `flow_run()` on your selection.

## Installation

Install with:

``` r
devtools::install_github("moodymudskipper/flow")
```
## Example

```{r, eval=FALSE}
library(flow)
flow_view(median.default)
```


```{r, setup, include=FALSE}
library(nomnoml)
```

```{nomnoml, echo=FALSE}
#.if: visual=rhomb fill=#e2efda align=center
#.for: visual=rhomb fill=#ddebf7 align=center
#.repeat: visual=rhomb fill=#fce4d6 align=center
#.while: visual=rhomb fill=#fff2cc align=center
#.standard: visual=class fill=#ededed
#.commented: visual=class fill=#ededed
#.header: visual=ellipse fill=#d9e1f2 align=center
#.return: visual=end fill=#70ad47  empty
#.stop: visual=end fill=#ed7d31  empty
#.break: visual=receiver fill=#ffc000 empty
#.next: visual=transceiver fill=#5b9bd5  empty
#arrowSize: 1
#bendSize: 0.3
#direction: down
#gutter: 5
#edgeMargin: 0
#edges: hard
#fill: #eee8d5
#fillArrows: false
#font: Calibri
#fontSize: 12
#leading: 1.25
#lineWidth: 3
#padding: 16
#spacing: 40
#stroke: #33322E
#title: filename
#zoom: 1
#acyclicer: greedy
#ranker: network-simplex
[<header>median.default(x, na.rm = FALSE, ...)]  -> [<if> 1: ;if (is.factor(x) \|\|
 is.data.frame(x))]
[<if> 1: ;if (is.factor(x) \|\|
 is.data.frame(x))] y -> [<standard> 2: ;stop("need numeric data")]
[<standard> 2: ;stop("need numeric data")]  -> [<stop> -2]
[<if> 1: ;if (is.factor(x) \|\|
 is.data.frame(x))] n -> [<end> -1]
[<end> -1]  -> [<if> 3: ;if (length(names(x)))]
[<if> 3: ;if (length(names(x)))] y -> [<standard> 4: ;names(x) <- NULL]
[<standard> 4: ;names(x) <- NULL]  -> [<end> -3]
[<if> 3: ;if (length(names(x)))] n -> [<end> -3]
[<end> -3]  -> [<if> 5: ;if (na.rm)]
[<if> 5: ;if (na.rm)] y -> [<standard> 6: ;x <- x\[!is.na(x)\]]
[<standard> 6: ;x <- x\[!is.na(x)\]]  -> [<end> -5]
[<if> 5: ;if (na.rm)] n -> [<if> 7: ;if (any(is.na(x)))]
[<if> 7: ;if (any(is.na(x)))] y -> [<standard> 8: ;return(x\[FALSE\]\[NA\])]
[<standard> 8: ;return(x\[FALSE\]\[NA\])]  -> [<return> -8]
[<if> 7: ;if (any(is.na(x)))] n -> [<end> -7]
[<end> -7]  -> [<end> -5]
[<end> -5]  -> [<standard> 9: ;n <- length(x)]
[<standard> 9: ;n <- length(x)]  -> [<if> 10: ;if (n == 0L)]
[<if> 10: ;if (n == 0L)] y -> [<standard> 11: ;return(x\[FALSE\]\[NA\])]
[<standard> 11: ;return(x\[FALSE\]\[NA\])]  -> [<return> -11]
[<if> 10: ;if (n == 0L)] n -> [<end> -10]
[<end> -10]  -> [<standard> 12: ;half <- (n + 1L)%/%2L]
[<standard> 12: ;half <- (n + 1L)%/%2L]  -> [<if> 13: ;if (n%%2L == 1L)]
[<if> 13: ;if (n%%2L == 1L)] y -> [<standard> 14: ;sort(x, partial = half)\[half\]]
[<standard> 14: ;sort(x, partial = half)\[half\]]  -> [<end> -13]
[<if> 13: ;if (n%%2L == 1L)] n -> [<standard> 15: ;mean(sort(x, partial = half + 0L:1L)\[half + 0L:1L\])]
[<standard> 15: ;mean(sort(x, partial = half + 0L:1L)\[half + 0L:1L\])]  -> [<end> -13]
[<end> -13]  -> [<return> 16]
```

