---
title: "Draw a function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Draw a function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Your first diagram

We use the function `flow_view()` to draw a function as a diagram. It can be any
function, packaged or user made, as long as it has a body.

Take the `rle` function from base R, it's role is to (from `?rle`):

> Compute the lengths and values of runs of equal values in a vector

And its code is :

```{r}
rle
```

The function is decently simple but its logic and complexity are not obvious at
a glance. `flow_view()` helps us sort it out.

```{r, fig.width=8, fig.height=8, fig.align = "center"}
library(flow)
flow_view(rle)
```

`if` statements always branch on 2 paths, whether an `else` clause is present
or not. `for`, `while`, and `repeat` loops are also supported.

The colored circles are exit point, orange for errors (using `stop()`), 
green for returned values (using `return()`) or just reaching the end of the function.

There you go, you know all you need to get started! And for this example and many 
this will be pretty much all you need. 

For other cases we propose the following features.

## Export to pdf, png, jpg, or html

*{flow}* supports saving your diagrams to various formats by using the argument `out`.

If `out` is a path (absolute or relative), the diagram will be saved there, 
using the file extension to determine the format. For instance :

```{r, eval = FALSE}
flow_view(rle, out = "diagrams/rle.png")
```

if you don't want to save at a specific location but just want to open your
diagram in a different format, use the shorthands `"pdf"`, `"png"`, `"jpg"`,
`"jpeg"`, `"htm"` , `"html"` and `flow_view()` will save them to a temporary 
location, print its url, and opens this location using `browseURL` (which opens
your files with your relevant default viewer). For instance.

```{r, eval = FALSE}
flow_view(rle, out = "html")
#> The diagram was saved to '*******.html'
#> [1] "*******.html"
```

When exporting to *html*, you might sometimes want to use SVG rendering by
using the argument `svg = TRUE`. A difference is that it makes text selectable.

## limitations

`next` and `break` statements are not considered special for the moment, so
they don't branch correctly. This should be solved in the future.

`stopifnot()` is not considered special, so it won't branch to an orange circle.



