---
title: "Simple Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

*{flow}*'s 2 main functions are `flow_view()` and `flow_run()`, which require only one argument for the simplest use cases.

```{r setup}
library(flow)
```

## `flow_view()`

`flow_view()` is used to display the logic of a function, a one item named list containing a function, a script or a quoted
expression.

```{r}
# display a function's body
flow_view(ave) 

# if non standard evaluation is an issue, use a one element named list
fun <- ave
flow_view(list(ave = fun))

# display script
flow_view("../tests/testthat.R")

# display quoted expression
flow_view(quote(if(1 + 1 == 2) {"ok"} else {"oh no"}))
```

`if` statements always branch into two paths, whether an `else` clause is present
or not. `for`, `while`, and `repeat` loops are also supported.

The colored circles are exit points, orange for errors (using `stop()`), 
green for returned values (using `return()`) or just reaching the end of the function.

If you installed *{plantuml}* you can set `engine` to `"plantuml"`, *plantuml* 
diagrams are a bit less flexible but they often look more polished and compact.

```{r}
# display a function's body
flow_view(ave, engine = "plantuml") 
```

## `flow_run`

`flow_run` actually executes a call to a function, and displays the logical path.
It takes as a first argument an unquoted call to the function we want to dive in.

```{r}
factorial <- function(x) {
  if(!is.integer(x)) stop("`x` must be integer!")
  res <- 1
  for(i in 2:x) {
    res <- res * i
    if(res > 1000) stop("too big!!!") 
  }
  res
}
```


```{r}
flow_run(factorial(5L))
```

It can also be used on calls that fail, which is convenient for debugging.

If you call `flow_run()` on a call to an S3 generic, the appropriate S3 method
will be represented.

Visualize which logical path is taken by a call (if calling a S3 generic as 
below, the relevant S3 method is presented):

```{r, eval=TRUE}
vec <- c(1:3, NA)
flow_run(median(vec, na.rm = TRUE))
```
