---
title: "Export Diagrams"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Export Diagrams}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(flow)
```

By default diagrams are shown in the viewer window. This might be enough,
especially if you are lucky enough to have a touch screen to zoom in and out on the relevant subparts, but you might want to export your diagram
to share it or to explore it more conveniently.

This is done by using the `out` parameter of `flow_view()` and `flow_run()`.

The format will be inferred from the file extension so you might do :

```{r, eval = FALSE}
library(flow)
flow_view(ave, out = "ave.png")
flow_view(ave, out = "ave.html")
flow_view(ave, out = "some_folder/ave.pdf")
flow_view(ave, out = "C:/some_folder/ave.jpeg")
```

If your goal is to explore rather than archive you might want to use
the following shorthands, which will save the output as a temp file and
open it with your default application.

```{r, eval = FALSE}
flow_view(ave, out = "png")
flow_view(ave, out = "html")
flow_view(ave, out = "pdf")
flow_view(ave, out = "jpeg")
```
