---
title: "Document a Whole Package with `flow_doc`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Document a Whole Package with `flow_doc`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `flow_doc()` function provides a way to draw all the functions of a package
and store them in an *html* report.

The `pkg` argument can be any package name, from base R, CRAN, or other 
including your local packages.

The `out` argument must be a path to an *html* or *md* file.

If you don't provide nor `pkg` nor `out`, a `diagrams.md` file will be created
at the root of your project folder, so that you can use `pkgdown::build_site`
to knit it into a new section after editing the YAML file properlu.

The [Diagrams](https://moodymudskipper.github.io/flow/articles/Draw-a-function.html)
section of the [website](https://moodymudskipper.github.io/flow/)
was built this way, simply by using the following call :

```{r, eval = FALSE}
library(flow)
flow_doc(prefix = "##")
```

And the `_pkgdown.yml` file that is created by `usethis::use_pkgdown()` is edited
to contain :

```
navbar:
  structure:
    left:  [home, reference, articles, news, diagrams]
    right: [github]
  components:
    home: ~
    diagrams:
     text: Diagrams
     href: diagrams.html
```
